SAT Competition 2020\tnoteref{title}

### 2021-06-28 paper/main.tex
minor rerewordings

The proofs were validated in a two-step fashion. First, the tool {\tt DRAT-trim}~\cite{DRATtrim}
was used for initial checking and optimizing the emitted proof, deriving a so-called LRAT proof file.
Afterwards, an independent formally-verified checker {\tt cake\_lpr} \cite{cakeLprGithub}
was used for validating the LRAT proof as a correct proof of unsatisfiability of the given formula.
In the Main track, only those unsatisfiable benchmark instances for which the proof emitted by a specific solver
could be validated by {\tt DRAT-trim} were considered solved by the  solver.
It should be noted that, while there were several cases where {\tt cake\_lpr} ran out of resources before 
there was no case where {\tt DRAT-trim} would accept
a proof and {\tt cake\_lpr} would later disagree with the verdict.
\textcolor{red}{This is pretty vague... does not really say if there were proofs that could not be validated with DRAT-trim??}

@@

\section{Main Track}

@@

\emph{Stable AllUip} resolves additional clauses beyond the First Unit Implication Point (1-UIP) and keeps them whenever they are of smaller size or LBD than the 1-UIP clause. 
By monitoring the frequency of clauses which successfully pass that filter, the solver dynamically limits the amount of such extended learning attempts~\cite{Zhang:2001:ClauseLearning,Bacchus:SC2020}.
The \emph{Trail Saving} variant caches backtracked portions of the trail and uses them to restore decision levels during search if possible~\cite{Hickey:2020:TrailSaving}.

@@

\solver{Painless-MCOMSPS-STR} integrates the solver \solver{MapleCOMSPS} in the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless,Liang:2017:Maplecomsps}. 
The authors submitted a \solver{32} and a \solver{64} threaded variant, which altogether won three awards, achieving
 the first place overall, the best score on satisfiable and the second-best score on unsatisfiable instances. 
The \solver{32} threaded variant achieved slightly better scores than the \solver{64} threaded variant overall
Furthermore, 
 the \solver{32} threaded variants geared towards either satisfiable or unsatisfiable instances 
showed much better  than the the \solver{64} threaded variants. \textcolor{red}{Not sure if I got this right: did the submit variants of the solver geared specifically towards SAT and UNSAT, resp.? The writing was really confusing here...}
% such that the runner-up solvers outperformed the \solver{64} threaded variant.

>>>>

Each unsatisfiability proof produced by 
each solver was validated in a two-step fashion. First, the tool {\tt DRAT-trim}~\cite{DRATtrim} was used for initial checking and optimizing the 
 proof, thereby obtaining a so-called LRAT proof file. 
An independent formally-verified checker {\tt cake\_lpr} \cite{cakeLprGithub} was then used for validating the 
LRAT proof as a correct proof of unsatisfiability.

In a few cases {\tt DRAT-trim} ran into the verification timeout of 40,000 seconds. 
In the Main track, only those unsatisfiable benchmark instances for which the proof produced by a solver 
could be validated at least by {\tt DRAT-trim} were considered solved by the solver. 
While there were several cases where {\tt cake\_lpr} ran out of resources, 
there was no case where {\tt DRAT-trim} would accept a proof and {\tt cake\_lpr} would not.

@@

\subsection{Main Track}

@@

\emph{Stable AllUip} resolves additional clauses beyond the First Unit Implication Point (1-UIP) and keeps them whenever they are of smaller size and their 
LBD not greater than that of the 1-UIP clause. 
By monitoring the frequency of clauses which successfully pass that filter, the solver dynamically limits the amount of such extended learning attempts~\cite{Zhang:2001:ClauseLearning,Bacchus:SC2020}.
The \emph{Trail Saving} variant caches backtracked portions of the trail and uses them to restore decision levels during search if possible~\cite{Hickey:2020:TrailSaving}.

@@

\solver{Painless-MCOMSPS-STR} integrates the solver \solver{MapleCOMSPS} in the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless,Liang:2017:Maplecomsps}. 
The authors submitted a \solver{32} and a \solver{64} threaded variant, which altogether won three awards, achieving the first place overall, the best score on satisfiable and the second-best score on unsatisfiable instances. 
Interestingly, the \solver{32} threaded variant performed better than the \solver{64} threaded variant.
